---
title: "Developing_Data_Product_Week_2_Assignment"
author: "Choong-Hoon Hyun"
date: "2023-01-02"
output: html_document
---

## Executive Summary
We will creat a web page using R Markdown that features a map created with Leaflet. I will display four tourist attractions in Seoul with "popup" text describing the name of the attractions. 

### Load leaflet package
```{r load leaflet package, echo = TRUE}
library(leaflet)
```

### Add markers to the map with popup text
```{r}
my_map <- leaflet() %>%
    addTiles() %>%
    addMarkers(lat = 37.5796, lng = 126.9770, popup = "Gyeongbookgung Palace") %>%
    addMarkers(lat = 37.574331036, lng = 126.98832938, popup = "Changdeoggung Palace (Secret Garden)") %>%
    addMarkers(lat = 37.5512, lng = 126.9882, popup = "Seoul Tower") %>%
    addMarkers(lat = 37.5559, lng = 126.9723, popup = "Seoul Station")

my_map
```

Four tourist attractions are displayed on an interactive map. They are Gyeongbookgung Palace, Changdeoggung Palace (Secret Garden), Seoul Tower, and Seoul Station.